Stack Safety as a Security Property

### 2020-07-09 main.tex
wibbles

 \[\mathit{Cof}(\mach,n)(\component) =
  \begin{cases}
    (\LOWSEC,\HIGHINT) & \text{if } \component \in \WORDS
                         \text{ and } \codemap(\component) = \funid \text{ for some }\funid\\
    (\HIGHSEC,\LOWINT) & \text{else if } \component \in \WORDS
                          \text{ and } \component \geq \mach(\SP)
                          \text{ or if } \component = \rout\\
    (\HIGHSEC,\HIGHINT) & \text{else if } \component \in \WORDS
                          \text{ and } \component \leq \mach(\SP) \negate  n \\
    (\LOWSEC,\LOWINT) & \text{else} \\
  \end{cases}\]

Going back to our running example, here is the state of the machine at
the call from {\tt main} to {\tt g}, showing addresses annotated with their
corresponding labels (not shown: the labels of the instructions
corresponding to {\tt g} that are $(\LOWSEC, \HIGHINT)$ instead of
$(\HIGHSEC, \HIGHINT)$)\apt{see previous note}:
\vspace*{0.2em}
% At Call to G
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{43.5em}{2em}{\SP}
\memory{3}{\instrc}[{\makebox[0pt]{$(\HIGHSEC,\HIGHINT)$}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{\emptyoutc}[{\makebox[0pt]{$(\HIGHSEC, \LOWINT)$}}]%
\memory{2}{\fprivc}[{\makebox[0pt]{$(\HIGHSEC, \HIGHINT)$}}]%
\memory{2}{\fcallc}[{\makebox[0pt]{$(\LOWSEC, \LOWINT)$}}]%
\memory{6}{\unusedc}[{\makebox[0pt]{$(\HIGHSEC, \LOWINT)$}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{42}
\MemoryLabel{-42.5em}{0.75em}{0}
\MemoryLabel{-38.5em}{0.75em}{0}
\MemoryLabel{-34.5em}{0.75em}{0}
\\
\end{center}

@@

Let \(\contour\) be a contour and \(\MPT\) be a (potentially infinite)
\(\MPOTRACE\). We will say \(\MPT\) satisfies {\em trace integrity} with
respect to \(\contour\) if its final state (if any) agrees with its
initial one on all components marked \(\HIGHSEC\) in \(\contour\):
%
\[\begin{split}
  \propdef{TraceInt} ~ \contour ~ \MPT \triangleq &
    \mpostate{\mach_e}{\pol_e}{\obs_e} = \head(\MPT) \Rightarrow \\
  & \mpostate{\mach_r}{\pol_r}{\obs_r} = \last(\MPT) \Rightarrow \\
  & \forall \component. ~ \contour(\component) = \HIGHSEC \Rightarrow
    \mach_e(\component) = \mach_r(\component) \\
\end{split}\]
\sna{Experimenting with font on the mathy version of the property.}

>>>>

 \[\mathit{Cof}(\mach,n)(\component) =
  \begin{cases}
    (\LOWSEC,\HIGHINT) & \text{if } \component \in \WORDS
                         \text{ and } \codemap(\component) = \funid \text{ for some }\funid\\
    (\HIGHSEC,\LOWINT) & \text{else if } \component \in \WORDS
                          \text{ and } \component \geq \mach(\SP)
                          \text{ or } \component = \rout\\
    (\HIGHSEC,\HIGHINT) & \text{else if } \component \in \WORDS
                          \text{ and } \component \leq \mach(\SP) \negate  n \\
    (\LOWSEC,\LOWINT) & \text{else} \\
  \end{cases}\]

Going back to our running example, here is the state of the machine at
the call from {\tt main} to {\tt g}, showing addresses annotated with their
corresponding labels:
\vspace*{0.2em}
% At Call to G
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{43.5em}{2em}{\SP}
\memory{3}{\instrc}[{\makebox[0pt]{$(\HIGHSEC,\HIGHINT)$}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{\emptyoutc}[{\makebox[0pt]{$(\HIGHSEC, \LOWINT)$}}]%
\memory{2}{\fprivc}[{\makebox[0pt]{$(\HIGHSEC, \HIGHINT)$}}]%
\memory{2}{\fcallc}[{\makebox[0pt]{$(\LOWSEC, \LOWINT)$}}]%
\memory{6}{\unusedc}[{\makebox[0pt]{$(\HIGHSEC, \LOWINT)$}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{42}
\MemoryLabel{-42.5em}{0.75em}{0}
\MemoryLabel{-38.5em}{0.75em}{0}
\MemoryLabel{-34.5em}{0.75em}{0}
\\
\end{center}

@@

Let \(\contour\) be a contour and \(\MPT\) be a (potentially infinite)
\(\MPOTRACE\). We say \(\MPT\) satisfies {\em trace integrity} with
respect to \(\contour\) if its final state (if any) agrees with its
initial one on all components marked \(\HIGHSEC\) in \(\contour\):
%
\[\begin{split}
  \propdef{TraceInt} ~ \contour ~ \MPT \triangleq &
    \mpostate{\mach_e}{\pol_e}{\obs_e} = \head(\MPT) \Rightarrow \\
  & \mpostate{\mach_r}{\pol_r}{\obs_r} = \last(\MPT) \Rightarrow \\
  & \forall \component. ~ \contour(\component) = \HIGHSEC \Rightarrow
    \mach_e(\component) = \mach_r(\component) \\
\end{split}\]
\sna{Experimenting with font on the mathy version of the property.}
